Robotic Cart System

### 2021-05-10 parts/10-introduction.tex
Minor updates

%----------------------------------------------------------------------
\section{Report Organization}
%----------------------------------------------------------------------
\begin{itemize}
    \item Chapter \ref{ch: intro} discusses the background and goals of the project and what other similar projects have accomplished.
    \item Chapter \ref{ch: sysDesign} explains how the robotic cart system in this project is broken down fundamentally, the components used to build the robot, and the algorithms used to control the robot.
    \item Chapter \ref{ch: implementation} discusses the implementation of all the parts onto the robot and the experimental results obtained when running the robot.
    \item Chapter \ref{ch: conclusionAndFuture} concludes the project work and discusses future endeavors on this project.
    \item Appendix \ref{ch: coppSimModeling} goes through the steps to build and simulate the Budget Bot chassis in CoppeliaSim
\end{itemize}

>>>>

%----------------------------------------------------------------------
\section{Report Organization}
%----------------------------------------------------------------------
\begin{itemize}
    \item Chapter \ref{ch: intro} discusses the background and goals of the project and what other similar projects have accomplished.
    \item Chapter \ref{ch: sysDesign} explains how the robotic cart system in this project is broken down fundamentally, the components used to build the robot, and the algorithms used to control the robot.
    \item Chapter \ref{ch: implementation} discusses the implementation of all the parts onto the robot and the experimental results obtained when running the robot.
    \item Chapter \ref{ch: conclusionAndFuture} concludes the project work and discusses future endeavors on this project.
    \item Appendix \ref{ch: coppSimModeling} goes through the steps to model and simulate the Budget Bot chassis in CoppeliaSim
    \item Appendix \ref{ch: assemblyInstructions} gives the step-by-step procedure for assembling the robot
\end{itemize}

### 2021-05-10 parts/20-system_architecture.tex
Updated chapter labeling
Added assembly instructions appendix
Minor updates

%======================================================================
\chapter{System Architecture}
\label{ch: Chapter2}
%======================================================================

@@

%----------------------------------------------------------------------
\section{Customized Reflector Array}
%----------------------------------------------------------------------
The XBee RF modules that were used are omnidirectional. In this project, however, it is desired to have differences in the received signals based on the angle from which the signal is coming. Therefore, one of the major components of this project is the reflector array that enables the XBee modules to be direction sensitive. This section discusses the steps that were taken to construct such a reflector array.

@@

%----------------------------------------------------------------------
\section{Localization and Navigation}
%----------------------------------------------------------------------

@@

\subsection{Navigation Algorithm}
The navigation algorithm is used to drive the robot toward the remote. The inputs to the navigation algorithm are the angle to the remote ($\theta_r$) and the distance to the remote ($d_r$). A target point is then calculated as the point that is in the same direction as the remote, but closer to the robot by a fixed following distance ($d_{follow}$), as shown in Fig. \ref{fig:navAlgoDiagram}. The distance to the target point is calculated as $d_{tgt} = d_r - d_{follow}$, and the angle to the target point is $\theta_{tgt} = \theta_r$. The linear and angular speeds of the robot ($v$ and $\omega$, respectively) are then calculated using proportional control by the following equations:
$$v = K_vd_{tgt}$$
$$\omega = K_\omega\theta_{tgt}$$
The appropriate duty cycles are then calculated as specified in section \ref{subsec:robotModel} and applied to the wheel motors.
\begin{figure}[H]
    \centering
    \begin{subfigure}{0.45\textwidth}
        \centering
        \includegraphics[width=0.95\textwidth]{figs/navigationAlgorithmDiagram.pdf}
        \caption{Target Point Diagram}
        \label{fig:navAlgoDiagram}
    \end{subfigure}%
    \begin{subfigure}{0.55\textwidth}
        \centering
        \includegraphics[width=0.95\textwidth]{figs/navigationAlgorithmFlowchart.pdf}
        \caption{Flowchart}
        \label{fig:navAlgoFlowchart}
    \end{subfigure}
    \caption{Navigation Algorithm Details}
    \label{fig:navAlgoDetails}
\end{figure}

>>>>

%======================================================================
\chapter{System Design}
\label{ch: sysDesign}
%======================================================================

@@

%----------------------------------------------------------------------
\section{Customized Reflector Array}\label{sec:customReflector}
%----------------------------------------------------------------------
The XBee RF modules that were used are omnidirectional. In this project, however, it is desired to have differences in the received signals based on the angle from which the signal is coming. Therefore, one of the major components of this project is the reflector array that enables the XBee modules to be direction sensitive. This section discusses the steps that were taken to construct such a reflector array.

@@

%----------------------------------------------------------------------
\section{Localization and Navigation Algorithms}\label{sec:locAndNavAlgos}
%----------------------------------------------------------------------

@@

\subsection{Navigation Algorithm}\label{subsec:navAlgo}
The navigation algorithm is used to drive the robot toward the remote. The inputs to the navigation algorithm are the angle to the remote ($\theta_r$) and the distance to the remote ($d_r$). A target point is then calculated as the point that is in the same direction as the remote, but closer to the robot by a fixed following distance ($d_{follow}$), as shown in Fig. \ref{fig:navAlgoDiagram}. The distance to the target point is calculated as $d_{tgt} = d_r - d_{follow}$, and the angle to the target point is $\theta_{tgt} = \theta_r$. The linear and angular speeds of the robot ($v$ and $\omega$, respectively) are then calculated using proportional control by the following equations:
$$v = K_vd_{tgt}$$
$$\omega = K_\omega\theta_{tgt}$$
The appropriate duty cycles are then calculated as specified in section \ref{subsec:robotModel} and applied to the wheel motors.
\begin{figure}[H]
    \centering
    \begin{subfigure}{0.45\textwidth}
        \centering
        \includegraphics[width=0.95\textwidth]{figs/navigationAlgorithmDiagram.pdf}
        \caption{Target Point Diagram}
        \label{fig:navAlgoDiagram}
    \end{subfigure}%
    \begin{subfigure}{0.55\textwidth}
        \centering
        \includegraphics[width=0.95\textwidth]{figs/navigationAlgorithmFlowchart.pdf}
        \caption{Flowchart}
        \label{fig:navAlgoFlowchart}
    \end{subfigure}
    \caption{Navigation Algorithm Details}
    \label{fig:navAlgoDetails}
\end{figure}
